---
title: "PQ"
author: "Yigit Ozan Berk"
date: "7/30/2019"
output: html_document
---


“Is there an association between college major category and income?”


Major_code'a gore dagilima bakilacak

possible confounders:
- perc_men & perc_women
- perc_employed

perc_employed icinde
- perc_employed_fulltime
- perc_epmloyed_fulltime_yearround

- perc_college_jobs
- perc_low_wage_jobs



outcome = income : p25th, median, p75th
predictor = major_category

butun variable'lari percentage olan kolonlardan almam lazim lineerligi korumak icin



# p25th

```{r}
sumCoef <- summary(lm(p25th ~ major_category - 1, data = mycol))
sumCoef
```


```{r}
summary(lm(p25th ~ major_category + perc_women - 1, data = mycol))
```

```{r}
summary(lm(p25th ~ major_category * perc_women - 1, data = mycol))
```


```{r}
summary(lm(p25th ~ perc_employed * major_category - 1, data = mycol))
```

setting up the regression data frames

```{r}
myp <- mycol[, c(4, 5, 6, 7, 8, 9, 10, 12, 13, 15, 17, 19)]
myp25 <- myp[, -c(6, 7)]
myp50 <- myp[, -c(5, 7)]
myp75 <- myp[, -c(5, 6)]
```

```{r}
fit1 <- lm(p25th ~ perc_employed + perc_college_jobs + perc_low_wage_jobs, data = myp25)
summary(fit1)
```

```{r}
summary(lm(p25th ~ perc_employed + perc_college_jobs, data = myp25))
```

```{r}
summary(lm(p25th ~ perc_employed, data = myp25))
```

```{r}
myp$sample_perc = myp$sample_size/myp$total
head(myp)
```

```{r}
fit2 <- lm(p25th ~ major_category * sample_perc - 1, myp)
summary(fit2)
```


```{r}
fit3 <- lm(p25th ~ major_category + perc_women + major_category * perc_women - 1, myp)
summary(fit3)
```

```{r}
fit4 <- lm(p25th ~ major_category + perc_women + major_category * perc_women + perc_college_jobs - 1, myp)
summary(fit4)
```

percentage of college jobs or percentage of women is not statistically significant confounders

```{r}
fit5 <- lm(p25th ~ major_category  - 1, myp)
summary(fit5)
```

